Supplemental information

### 2017-10-27 manuscript/supplemental.tex
fixed some compiling errors, supplemental still isn't perfect

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
      \# Remove extra data on parasitoids, etc.\\
      prior\_web\_data[,31:57]\textless-NULL\\
      prior\_web\_data[,4:26]\textless-NULL\\
      prior\_web\_data[,2]\textless-NULL\\
      \# Build a web with interactions=1 for any galler observed on any genotype\\
      prior\_web=matrix(nrow=26,ncol=4)\\
      for(r in 1:length(levels(prior\_web\_data\$Genotype)))\{\\
      \hspace{4pt}  gen=levels(prior\_web\_data\$Genotype)[r]\\
      \hspace{4pt}  subset=prior\_web\_data[which(prior\_web\_data\$Genotype==gen),]\\
      \hspace{4pt}  for(c in 1:4)\{\\
      \hspace{8pt}    if(sum(subset[,2+c])\textgreater0)\{\\
      \hspace{12pt}      prior\_web[r,c]=1\\
      \hspace{8pt}    \} else \{\\
      \hspace{12pt}      prior\_web[r,c]=0\\
      \hspace{8pt}    \}\}\}
      \# Remove non-interactive genotype
      prior\_web<-prior\_web[which(rowSums(prior\_web)\textgreater0),]
      }

@@

@@

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} 
      prior\_web\_data=read.csv('tree\_level\_interaxn\_all\_plants\_traits\_size.csv')\\
      prior\_web\_data <- prior\_web\_data[,8:26]

      \# Build a web with interactions=1 for any parasitoid on any galler
      prior\_web=data.frame()

      \# each column contains all interactions for a particular parasitoid-galler combination
      for(column in 1:ncol(prior\_web\_data)){
      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall
      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")
      \hspace{-4pt}   galler = galler\_emerged[[1]][1]
      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]

      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)
      \hspace{-4pt}   linkstrength = sum(prior\_web_data[,column])
      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] <- linkstrength
      }

      \# Make the naS into 0
      prior\_web[is.na(prior\_web)] <- 0

      \# remove emerging gallers with no parasitoids
      prior\_web\_para\_only <- prior\_web[,c(2:6,8:9,12)]

      \# convert interaction strengths to 1
      prior\_web[which(prior\_web>0)] <- 1

      write.csv(prior\_web\_para\_only, file="prior\_web\_para\_only.csv", quote=F)
      }

>>>>

      \vspace{6pt}
      \emph{
      \noindent \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
      \# Remove extra data on parasitoids, etc.\\
      prior\_web\_data[,31:57]\textless-NULL\\
      prior\_web\_data[,4:26]\textless-NULL\\
      prior\_web\_data[,2]\textless-NULL\\
      \# Build a web with interactions=1 for any galler observed on any genotype\\
      prior\_web=matrix(nrow=26,ncol=4)\\
      for(r in 1:length(levels(prior\_web\_data\$Genotype)))\{\\
      \hspace{4pt}  gen=levels(prior\_web\_data\$Genotype)[r]\\
      \hspace{4pt}  subset=prior\_web\_data[which(prior\_web\_data\$Genotype==gen),]\\
      \hspace{4pt}  for(c in 1:4)\{\\
      \hspace{8pt}    if(sum(subset[,2+c])\textgreater0)\{\\
      \hspace{12pt}      prior\_web[r,c]=1\\
      \hspace{8pt}    \} else \{\\
      \hspace{12pt}      prior\_web[r,c]=0\\
      \hspace{8pt}    \}\}\}
      \# Remove non-interactive genotype
      prior\_web\textless-prior\_web[which(rowSums(prior\_web)\textgreater0),]
      }

@@

      \vspace{6pt}

@@

      \vspace{6pt}
      \noindent \emph{
      \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
      prior\_web\_data \textless- prior\_web\_data[,8:26]\\

      \# Build a web with interactions=1 for any parasitoid on any galler\\
      prior\_web=data.frame()\\

      \# each column contains all interactions for a particular parasitoid-galler combination\\
      for(column in 1:ncol(prior\_web\_data))\{\\
      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall\\
      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")\\
      \hspace{-4pt}   galler = galler\_emerged[[1]][1]\\
      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]\\

      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)\\
      \hspace{-4pt}   linkstrength = sum(prior\_web\_data[,column])\\
      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] \textless- linkstrength\\
      \} 
      \# Make the NAs into 0\\
      prior\_web[is.na(prior\_web)] \textless- 0\\
      \# remove emerging gallers with no parasitoids\\
      prior\_web\_para\_only \textless- prior\_web[,c(2:6,8:9,12)]\\
      \# convert interaction strengths to 1\\
      prior\_web[which(prior\_web\textgreater0)] \textless- 1\\
      write.csv(prior\_web\_para\_only, file=``prior\_web\_para\_only.csv", quote=F)
      }\par
